SAT Competition 2020\tnoteref{title}

### 2021-01-22 paper/main.tex
few sentences about small portfolios

\caption{Results of Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver}
\label{tab:cloud}

@@

\begin{table}[tb]
%\setlength\tabcolsep{2.5pt}%default: 6pt
%\renewcommand{\arraystretch}{1.03}%default: 1
%\smaller
\centering
\begin{tabularx}{\linewidth}{rXl}
\bf k & \bf k-Tuple & \bf Score\\ 
\hline\arrayrulecolor{lightgray}
1 & \{ \solver{Kissat-sat} \} & $3926.2$\\
\hline
2 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech} \} & $3160.5$\\
3 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020} \} & $2986.4$\\
4 & \{ \solver{Kissat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020}, \solver{Scavel01} \} & $2842.6$\\
5 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020}, \solver{Scavel01}, \phantom{\{ }\solver{CMS-Walksat} \} & $2757.3$\\
6 & \{ \solver{Kissat-sat}, \solver{Kissat-unsat}, \solver{Relaxed}, \solver{Relaxed-newTech}, \phantom{\{ }\solver{CaDiCaL-alluip-trail}, \solver{f2trc-s} \} & $2687.0$\\
7 & \{ \solver{Kissat-sat}, \solver{Kissat-unsat}, \solver{Relaxed}, \solver{Relaxed-newTech}, \phantom{\{ }\solver{CaDiCaL-alluip-trail}, \solver{f2trc-s}, \solver{CMS-Walksat}\} & $2616.9$\\
\hline
48 & \emph{set of all solvers} & $2431.4$
\end{tabularx}
\caption{Best performing k-tuples in terms of their VBS's PAR-2 score.}
\label{tab:tuples}
\end{table}

The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, 
which is much better than that of the single best solver  \solver{Kissat-sat} with a PAR-2 score of $3926.2$. 
We also calculated the PAR-2 score of the VBS of small subsets of the $48$ submitted solvers. 
In Table~\ref{tab:tuples}, we report on the best performing sets of solvers of fixed size $k \in \{1, \dots, 7\}$.

\subsection{Score per Instance Family}

\todo{Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth'' or ``timetable''. }

>>>>

\caption{Top 10 Solvers in Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver}
\label{tab:results}

@@

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{rXl}
\bf k & \bf Best k-Tuple & \bf Score\\ 
\hline\arrayrulecolor{lightgray}
1 & \{ \solver{Kissat-sat} \} & $3926.2$\\
\hline
2 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech} \} & $3160.5$\\
3 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020} \} & $2986.4$\\
4 & \{ \solver{Kissat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020}, \solver{Scavel01} \} & $2842.6$\\
5 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020}, \solver{Scavel01}, \phantom{\{ }\solver{CMS-Walksat} \} & $2757.3$\\
6 & \{ \solver{Kissat-sat}, \solver{Kissat-unsat}, \solver{Relaxed}, \solver{Relaxed-newTech}, \phantom{\{ }\solver{CaDiCaL-alluip-trail}, \solver{f2trc-s} \} & $2687.0$\\
7 & \{ \solver{Kissat-sat}, \solver{Kissat-unsat}, \solver{Relaxed}, \solver{Relaxed-newTech}, \phantom{\{ }\solver{CaDiCaL-alluip-trail}, \solver{f2trc-s}, \solver{CMS-Walksat}\} & $2616.9$\\
\hline
48 & \emph{Set of all Solvers} & $2431.4$
\end{tabularx}
\caption{Best performing k-tuples in terms of their VBS's PAR-2 score.}
\label{tab:tuples}
\end{table}

The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, which is much better than the PAR-2 score of $3926.2$ of the single best solver \solver{Kissat-sat}. 
Given the set of solvers $S$, the set of tuples of size $k$ is defined as follows $P_k := \{ T \mid T \in 2^S \land |T| = k\}$.
We calculated the PAR-2 score for each VBS created from solver tuples in $P_k$. 
In Table~\ref{tab:tuples}, we report on the single best performing $k$-tuple $T_k \in P_k$ ($1 \leq k \leq 7$).

Interestingly, each of the first five tuples $T_{k \leq 5}$ contains exactly one of the three \solver{Kissat} variants. 
For $i < 5$ the relation $T_{i} \subset T_{i+1}$ holds only under projection to base solvers due to the fluctuating variants of \solver{Kissat}. 
The composition changes more strongly in $T_6$. 
Interestingly, we now have both variants $\{ \solver{Kissat-sat}, \solver{Kissat-unsat} \} \subset T_6$, and moreover it holds that $T_6 \subset T_7$.
With the only exception being $\solver{Scavel01} \in T_6 \cap T_7$, all solvers in $T_1, \dots, T_7$ belong the top performing solvers in the Main track (cf. Table~\ref{tab:results}).

\subsection{Score per Instance Family} 
\todo{Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth'' or ``timetable''. }
